%!Mode::"TeX:UTF-8"
\documentclass[UTF8]{ctexart}
\usepackage[top=0.5in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{fancyhdr}
\title{IELTS writing 1}
\author{YANG Zhipeng}
\date{}
\begin{document}
\maketitle
\thispagestyle{empty}
\LARGE{\underline{Topic:}}

Fast food is now universally available in most countries and is becoming increasingly popular. Some feel that this is a positive trend, while others do not.

What are your opinions on this?

\LARGE{\underline{Writing:}}

According to my observations, more and more young people tend to have a meal in fast food restaurants. Some people believe that this kind of food has a positive influence in modern life because its convenience and low cost. However, I intend to argue that fast food is neither good for individuals nor society.

First of all, it is evident that consuming fast food leads to health problems. Because of the inavailability of fat and sugar in the primitive society, human love foods which have a huge quantity of energies. Evolutionary, Our body have adjusted to conserve more energies which can increase the proportion of survive. Yet, in our modern society, these energies are surplus -- We can get energies whenever we want. These surplus energies will cause diseases such as heart disease, high blood pressure. That's why in America, there's a huge proportion of people who are overweight. Moreover, even though fast food is affordable for most people and convenient enough, the cost of curing illnesses in later life is significant. Conclusively, the shortcomings of fast food are far more than its benefits. 

Furthermore and even more importantly, the problem that I described will cause a inegligible issue on our social security system. The people who have had a huge amount of fast foods may have many incurable diseases among their life. That is to say, our social security system will have to pay throughout their remaining life. In another word, once we pay too much on social security, we would not have enough resources to feed our next generation and support our development. Along with our aging society, this problem would become more and more severe.

By the way of conclusion, I hold an opinion that fast food becoming more and more popular would be a negative trend.
\end{document}
