%!Mode::"TeX:UTF-8"
\documentclass[UTF8]{ctexart}
\usepackage[top=0.5in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{fancyhdr}
%\renewcommand{\baselinestretch}{2}
\title{IELTS writing 2}
\author{YANG Zhipeng}
\date{}
\pagestyle{fancy}
\begin{document}
\maketitle
\noindent
\LARGE{\underline{Topic:}}

\normalsize{In most countries multinational companies and their products are becoming more and more important.

This trend is seriously damaging our quality of life.

What are your opinions on this?}

\noindent
\LARGE{\underline{Writing:}}

\normalsize{Nowadays, multinational companies are becoming more and more important all over the world. Often, we call them globalization. However, some people think that globalization may have some negative impact to our life. Yet, I don't agree with their opinions in three main areas.

Firstly, due to our uneven development world, the cost of manufacturing in different parts of world are different. In some developing countries, especially in China, the cost of labour are incredibly lower than in developed countries. As a result, building factories in developing countries then manufacturing products can maximize the efficiency manufacturing products. Therefore, consumers could purchase cheaper 
products. In addition, because of cheaper products, the people who are poor could live a better life.

That brings me to my second point, manufacturing products in developing countries can help people in developing countries to enjoy modern life. What if we don't build factories and don't trade with developing countries? The people there may not found a job, therefore they will maintain poor and won't have any chance modern products. Perhaps things will get even worse, according to the lack of jobs, it might cause a 
civil war which may cause humanitarian crisis.

Last but not least, multinational companies will not only reduce the price of products but also increase the income of employees who work in 
developed countries. On the one hand, building factories in other countries can lower the cost of producing. On the other hand, selling
products in other countries can also maximize the revenue of a company. So that the company can offer more salaries to their employees.

Multinational companies is a kind of multinational cooperation which could not only maximize the efficiency of production 
but also maximize the revenue of a company as well as their employees. Consequently, my conclusion is globalization will improve our life
quality.}
\end{document}
